Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2018-04-29 poster/main.tex
add references to poster

\nocite{*} % Insert publications even if they are not cited in the poster
\small{\bibliographystyle{unsrt}
\bibliography{sample}\vspace{0.75in}}

@@

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\setbeamercolor{block title}{fg=red,bg=white} % Change the block title color

%----------------------------------------------------------------------------------------
%	CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\setbeamercolor{block alerted title}{fg=black,bg=norange} % Change the alert block title colors
\setbeamercolor{block alerted body}{fg=black,bg=white} % Change the alert block body colors

\begin{alertblock}{Contact Information}

\begin{itemize}
\item Web: \href{http://www.university.edu/smithlab}{http://www.university.edu/smithlab}
\item Email: \href{mailto:john@smith.com}{john@smith.com}
\item Phone: +1 (000) 111 1111
\end{itemize}

\end{alertblock}

>>>>

\nocite{*} % Insert publications even if they are not cited in the poster
\small{\bibliographystyle{unsrt}}
D.~Balduzzi and M.~Ghifary.
Strongly-typed recurrent neural networks.

G.~E. Blelloch.
Prefix sums and their applications.

J.~Bradbury, S.~Merity, C.~Xiong, and R.~Socher.
Quasi-recurrent neural networks.

N.~Kalchbrenner, et al.
Neural machine translation in linear time.

T.~Lei, Y.~Zhang,
Training RNNs as fast as CNNs.

A.~van~den Oord, et al.
Wavenet: A generative model for raw audio.

@@
